---
title: "prep_events_test"
author: "Luke Vawter"
date: "November 5, 2018"
output: html_document
---

```{r echo=FALSE}
knitr::opts_chunk$set(eval=evaluate, cache=cache.me)
```


L.V.: this is a modified version of prep_events created by Luke Vawter for use with VA_ODU data. DO NOT USE THIS SECTION if you are pulling data from CEDR.  Use the master branch of phyto which uses prep_events instead.

Phytoplankton sampling event data obtained from VA ODU ([Download Monitoring Event]) is imported.
```{r}
events.df <- data.table::fread(file.path(project.dir, "data/phytoplankton2/VA_ODU_phyto_event.csv"#cedr_phyto_event.csv"
                                         ),
                            data.table = FALSE,
                            na.strings = "")
```

Some of the salinity zones (`salzone`) differ from the categories in [@LacouturePhytoplanktonindexbiotic2006]. Salinity zones are converted to one of four categories: "f" (freshwater), "m" (mesohaline), "o" (oligohaline), and "p" (polyhaline).


```{r}
events.df <- events.df %>% 
  mutate(sampledate = as.Date(sampledate)) 
```


L.V.: script in development for resolving station salzone issues
```{r}
events_test.df <- events.df%>%

mutate(salzone = case_when(
    events_test.df$station %in% c("tf3.3","tf4.2","tf5.5")~ "F",
    #events_test.df$station == starts_with("cb")~ "good",
    events_test.df$station %in% c("ret3.1","ret4.3","ret3.1")~ "O",
    events_test.df$station %in% c("le3.6","le5.2","le5.4","le5.5-w")~ "P",
    TRUE~TRUE

  )
  )

```


L.V.: I initially thought this script was causing problems with salzone values beyond this point. Since then I've determined that the problem was originating elsewhere.  However it is a script that could cause problems for future data.  If you are running into issues with salzones(for f in particular) with newer data comment this code out and run it again would be a good first step.
```{r}
events.df <- events.df %>%
  mutate(sampledate = as.Date(sampledate),
         salzone = case_when(
           salzone %in% c("tf", "fe") ~ "f",
           salzone %in% c("m", "me") ~ "m",
           salzone %in% c("o", "oe") ~ "o",
           salzone %in% c("p", "pe") ~ "p",
           TRUE ~ as.character(NA)
         ))
```


Retain only unique information regarding the data provider (`source`), station name (`station`), sample date (`sampledate`), water layer (`layer`), and salinity zone (`salzone`).
```{r}
events.sub <- events.df %>% 
  select(source, station, sampledate, layer, salzone) %>% 
  distinct()
```

Import the salinity zone used by Jacqueline M. Johnson of the Chesapeake Bay Program. This will provide a check of salinity zone classification from 10 years ago to the salinity zone classification in CEDR.

```{r}
old.salzone <- readxl::read_excel(file.path(project.dir, "data/jackie_data/JMJ_PIBI_Salzone_Data.xlsx"),
                         sheet = "JMJ Salzone+Scores") %>% 
  clean_up() %>% 
  select(station, sample_date, ibi_salzone) %>% 
  mutate(sample_date = as.Date(sample_date)) %>% 
  rename(old_salzone = ibi_salzone,
         sampledate = sample_date) %>% 
  distinct()
```

L.V.: the following code was the source of the issue in which salzones were being removed.  This code is written specifically for the older data set and was confilicting with with VA ODU's structure.
I've commented it out.

<!-- Append the salinity zone defined by Jacqueline M. Johnson (`old_salzone`) to `wq.df`. -->
<!-- ```{r} -->
<!-- events.sub <- inner_join(events.sub, old.salzone, by = c("station", "sampledate")) -->
<!-- ``` -->

<!-- Identify rows where the salinity zone specified by CEDR (`salzone`) differs from the salinity zone specified by Jacqueline M. Johnson (`old_salzone`). -->
<!-- ```{r} -->
<!-- events.sub <- events.sub %>%  -->
<!--   mutate(salzone_disagree = if_else(salzone != old_salzone, TRUE, FALSE)) -->
<!-- ``` -->

<!-- Summarize and plot the differences in specified salinity zones. -->
<!-- ```{r} -->
<!-- salzone.diff <- events.sub %>%  -->
<!--   select(station, sampledate, source, salzone, old_salzone, salzone_disagree) %>%  -->
<!--   unite(sal_group, salzone, old_salzone) %>%  -->
<!--   distinct() %>%  -->
<!--   filter(salzone_disagree == TRUE) %>%  -->
<!--   group_by(sal_group) %>%  -->
<!--   summarize(count = n()) %>%  -->
<!--   ungroup() %>%  -->
<!--   arrange(count) %>%  -->
<!--   mutate(sal_group = factor(sal_group, levels = unique(sal_group))) %>%  -->
<!--   ggplot(aes(sal_group, count, fill = count)) +  -->
<!--   scale_fill_gradient(low = "lightblue", high = "darkblue") + -->
<!--   geom_bar(stat = "identity") + -->
<!--   xlab("Salinity Zone Disagreement") + -->
<!--   ylab("Number of Disagreements") -->
<!-- salzone.diff -->
<!-- ``` -->

<!-- To be consitent with the data used to develop the PIBI, salinity zones specified by Jacqueline M. Johnson (`old_salzone`) were favored when salinity zones differed. To be more explicit, `salzone` is replaced by `old_salzone` when salinity zones differed. -->
<!-- ```{r} -->
<!-- events.sub <- events.sub %>%  -->
<!--   rename(cedr_salzone = salzone) %>%  -->
<!--   mutate(salzone = if_else(salzone_disagree == TRUE, old_salzone, cedr_salzone)) -->
<!-- ``` -->

Join `bay.df` and `events.sub` to combine phytoplankton count data with event data.
```{r}
bay.df <- left_join(bay.df, events.sub, by = c("source", "station",
                                               "sampledate", "layer")) %>% 
  mutate(unique_id = paste(unique_id, season, salzone, sep = "_"))
```

